\Large{Adversarial Training against Systematic Uncertainty}

### 2016-10-24 tex/paper.tex
physics example (wip)

\subsection{Physics example}

>>>>

\subsection{High energy physics example}

In collisions at the Large Hadron Collider, massive particles can be produced at
such high energies that their decay products are collimated and the resulting
jets overlap. Still, deducing whether an observed jet is either due  to a single
hadronic particle or to the decay of a massive object into multiple hadronic
particles  is critical for understanding the nature of the particles produced in
the collision \citep{butterworth2008jet,guest2016jet}. More importantly, this
classification problem is often made difficult by the presence of simulatenous
interactions, known as pileup, which contributes significant energy depositions
unrelated to the particles of interest.

\begin{figure}
    \includegraphics[width=0.48\textwidth]{figures/ams.pdf}
    \vspace{-1cm}
    \caption{(to write)}
    \label{fig:physics-ams}
\end{figure}
